%!TEX program = xelatex
%!TEX spellcheck = en_GB
\documentclass[final]{report}
\input{../../.library/preamble.tex}
\input{../../.library/style.tex}
\addbibresource{../../.library/bibliography.bib}
\begin{document}
\chapter{Introduction}
\label{ch:introduction}

This project researches the toxicity in twitch streamer communities.
It is a well known problem in online gaming that users exert toxic behaviour to their team mates or the enemy team when things do not go as they want to.
Companies use their own detection algorithms to track and punish these toxic users accordingly.
This project focuses on the well known streamer site twitch.tv, which enables users and companies to broadcast their gameplay or tournaments.
A dataset was scraped from twitch and analysed for toxic behaviour by the viewers of popular streamers.
These streamers play well known games like League of Legends, CS:GO and Dota 2.
The goal of this report is to detect the influence of the streamer behaviour on its viewers and vice versa to see if toxicity can be passed from viewers to the streamer or the other way around. In the end this became too much work because of the training of the classifier. So this report mainly analyses the data gathered from the Twitch API.

In this report the following topics are discussed:
\begin{enumerate}
	\item \textbf{Related Work}, literature that is related to our project is briefly discussed and compared to what our project aims to achieve.
	\item \textbf{Data Gathering}, this section describes how we obtained our data using different tools available. It also describes the preprocessing of the data.
	\item \textbf{Data and Results}, some statistics of the dataset are described here together with an analysis  of the results.
	\item \textbf{Uncompleted Results}, in this section several parts that weren't completed yet are shown together with possible solutions for the future.
	\item \textbf{Conclusion}, conclusions that can be drawn from the data and results are presented here.
	%\item \textbf{Future Work}, if one wants to continue with this project several suggestions are shown to include in the future.
\end{enumerate}

\end{document}